e9_altsAnalysis

### 2015-10-17 analysis/e11_analysis.Rmd
adding copy of e10 analysis for e11

```{r}

@@

Data prep
---------
```{r}
files <- dir("production-results/e10/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e10/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}

>>>>

Experiment e11 - Pragmatic Listener experiment with alternatives
```{r}

@@

Data prep
---------
```{r}

# make sure to set directory path to 'production-results/e11/'
results_path = "sandbox-results/e11/"
files <- dir(results_path, pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste(results_path,f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}
